### 2017-02-23 doc/Thesis/data/theory.tex
Thesis: Addressing initial comments

>>>>

To derive the IQS equations, the time dependent neutron diffusion equation with delayed neutron precursors are presented by Equations~\ref{eq:flux}~and~\ref{eq:precursor}.

\begin{subequations}
\begin{multline}
\frac{1}{v^g}\frac{\partial \phi^g}{\partial t}  = 
\frac{\chi_p^g}{\keff} (1-\beta)\sum_{g'=1}^G  \nu^{g'} \Sigma_f^{g'} \phi^{g'} 
+ \sum_{g'\neq g}^G\Sigma_s^{g'\to g} \phi^{g'}  \\ + \sum_{i=1}^I\chi_{d,i}^g\lambda_i C_i 
-  \left( -\div D^g \grad  + \Sigma_r^g \right) \phi^g   
\ , \quad 1 \le g \le G 
\label{eq:flux}
\end{multline}
\be
\frac{dC_i}{dt} = \frac{\beta_i}{\keff}\sum_{g=1}^G\nu^{g} \Sigma_f^g \phi^{g} - \lambda_i C_i \ , \quad 1 \le i \le I 
\label{eq:precursor}
\ee
\end{subequations}

where,

\begin{longtable}{lll}
$\phi^g$   			&	$=$	&	Scalar flux in energy group $g$ \\
$C_i$					  &	$=$	&	Concentration of delayed neutron precursor $i$ \\
$\Sigma_f^{g}$	&	$=$	&	Fission cross section in energy group $g$ \\
$\Sigma_r^{g}$	&	$=$	&	Removal cross section in energy group $g$ \\
$\Sigma_s^{g' \to g}$	&	$=$	&	Scattering cross section from energy group $g'$ to $g$ \\
$v^g$					  &	$=$	&	Neutron velocity in energy group $g$ \\
$\chi_p^g$			&	$=$	&	Fission spectrum of prompt neutrons \\
$\chi_{d,i}^g$	&	$=$	&	Fission spectrum of delayed neutrons from precursor $i$ \\
$\nu^g$					&	$=$	&	Total number of neutrons per fission \\
$D^g$					  &	$=$	&	Diffusion coefficient in energy group $g$\\
$\lambda_i$			&	$=$	&	Decay constant of precursor $i$ \\
$\beta_i$				&	$=$	&	Delayed neutron fraction  from precursor $i$ \\
$\beta$			 	  &	$=$	&	Total delayed neutron fraction ($\beta = \sum_{i=1}^I \beta_{i}$) \\
  & & 
\end{longtable}

Most reactor computation frameworks, including Rattlesnake, discretize the time variable directly with these equations using a multitude of schemes (Implicit Euler, Crank-Nicholson, implicit Runge-Kutta, etc.).  In this paper, the method of discretizing Equations~\ref{eq:flux}~and~\ref{eq:precursor} is generally referred to as ``implicit discretization''.  This research intends to improve upon this method by instead implementing the improved quasi-static method (IQS) for neutron kinetics and
implement it within a multiphysics setting.
